Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
wip a2

Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$. The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$. If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
\begin{equation}
\begin{aligned}
	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
	&= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
\end{aligned}
\end{equation}
where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in \R$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function. Finally, we can write the first and second derivatives as follows

@@

>>>>

Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$. The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \mapsto \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$. If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
\begin{equation}
\begin{aligned}
	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
	&= - y_i \cdot \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
\end{aligned}
\end{equation}
where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)} \in [0, 1]$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function. Finally, we can write the first and second derivatives as follows

@@

% Big O
% train neural network
% compute the NTK -> from the NTK paper
% we outer product of the kzi O(NM^2)
% inversion O(M^3)

% Practical implementation
% mention that we do that in batches not full N 
% role of jitter 
% role of clamping
% GPU A100 Nvidia
